Globally-centered autocovariances in MCMC

### 2020-07-22 Paper/main.tex
Day one of clean-up ends

\usepackage{amssymb,amsthm,amsmath}
\usepackage{commath}
\usepackage{enumerate,xcolor}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{caption,setspace}
\usepackage{subcaption}
\DeclareMathOperator{\Tr}{Tr}
\newcommand{\dd}[1]{\mathrm{d}#1}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\text{Var}}
\newcommand{\Cov}{\text{Cov}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\B}{\mathcal{B}}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
% These three packages are from the American Mathematical Society and includes all of the important symbols and operations 
\usepackage{fullpage}
\usepackage{comment}
\usepackage[linesnumbered, ruled]{algorithm2e}
% By default, an article has some vary large margins to fit the smaller page format.  This allows us to use more standard margins.
\allowdisplaybreaks
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

@@

\begin{figure}[htbp]
\begin{subfigure}{\textwidth}
   \centering
   \includegraphics[width=.8\linewidth]{plots/gaussian-acf_n1e4.pdf}
   \caption{$n = 10^4$}
   \label{subfig:gauss-acf-1e4}
 \end{subfigure}\\
 \begin{subfigure}{\textwidth}
   \centering
   \includegraphics[width=.8\linewidth]{plots/gaussian-acf_n1e5.pdf} 
   \caption{$n = 10^5$}
   \label{subfig:gauss-acf-1e5}
 \end{subfigure}
 \caption{Autocorrelation plot for locally-centered ACF (left) and globally centered ACF (right) averaged over all chains. (a) $n = 10^4$, not converged yet; (b) $n =  10^5$, converged}
 \label{fig:gauss:acf}
\end{figure}
\end{example}

@@

 Suppose we have $m$ replications of Markov chains for same target distribution and $\{X_{st}; \; t \in \mathbb{Z}\}$ denote the $s^{th}$ Markov chain. Let the sample mean of $s^{th}$ Markov chain be denoted by $\bar{X}_s$ and the global mean by $\bar{\bar{X}} = \sum_{s = 1}^{m}\bar{X}_s/m$. The global mean provides a better estimate for the expectation value when the number of simulation per chain are not sufficient for the convergence to kick in. The globally-centered autocovariance function (G-ACF) for the $s^{th}$ Markov chain is given by:
%
\[
\hat{\Gamma}_{G}(k) = \dfrac{1}{mn} \sum_{s=1}^{m}\sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T
\]

@@

\subsection{Theoretical results} % (fold)
\label{sub:theoretical_results}

@@

The bias for G-ACF is similar to the bias of sample autocovariance estimator in case of single chain except for a few small order terms that shall be later addressed in theorem \ref{th:G-_expec}. Before getting to the bias results for $\hat{\Gamma}_{RAV}(k)$ for any lag $k$, we introduce an additional notation. For $q \geq 1$, we define
\[
\Phi^{(q)} = \sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma(k)\|
\]
We denote $\Phi^{(1)} \textrm{ by } \Phi$. 
\begin{theorem} \label{th:G-_expec}
   \[
   \mathbb{E}[\hat{\Gamma}_{G}(k)] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
   \]
\end{theorem}

\begin{proof}
 The estimator for autocovariance with divisor $n$ is suggested by \cite{parzen1961approach} for its lesser mean square error despite having greater bias than the unbiased estimator with an $n - \abs{k}$ divisor. 
 We know that $\hat{\Gamma}_s(k)$ is asymptotically unbiased with a $o(1)$ bias term that remains fixed for any $k$. The bias term is given by \cite{priestley1981spectral} as

 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)
 \end{equation}

By proposition 1 in \cite{song1995optimal} 
\begin{equation} \label{eq:song}
\Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
\end{equation}

As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. We can break $\hat{\Gamma}_{G-}$ into four parts for all $k \geq 1$ as:
 \[
 \hat{\Gamma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
 \]
%
where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$\\
The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms. The complete proof evaluating the expectation values of last three terms can be found in Appendix subsection \ref{appendix:bias}.
\end{proof}

\begin{remark} \label{rmrk:exp_G-f_minus_acf}
Using theorem \ref{th:G_expec} and equation \ref{eq:priestly},
\[
\mathbb{E}[\hat{\Gamma}_{G}(k) - \hat{\Gamma}(k)] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
\]
We know that the sample autocovariance $\hat{\Gamma}(k)$ underestimates the truth due to a negative bias of $\abs{k}\Gamma(k)/n$ for finite $n$. However, in practice, it is preferred to overestimate the autocovariance for finite $n$ than to underestimate it in order to have a more realistic idea about the correlation in a Markov chain at a particular lag.  Note that the RHS in the above expression is positive. As a consequence, G-ACF will counter this negative bias and give more reliable estimates for ACF.

\end{remark}

\begin{corollary} \label{cor:lag0_expectation}
\[
\mathbb{E}[\hat{\Gamma}_{G}(0)] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
\]
\end{corollary}

\begin{proof}
 The proof is in Appendix subsection \ref{appendix:bias}.
\end{proof}

@@

\begin{proof}
We complete the proof by showing that $\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij}$ converges to 0 almost surely for all $i,j \in \{1,...,p\}$ and $\tilde{\Sigma}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$. We will show that

\[
\hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} = g_1(n)D^2 + g_2(n)D + g_3(n)
\]
where $D$ is the finite random variable associated with SIP. We will show that
\begin{align*}
    g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2}\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right]
\end{align*}

Using $\psi(n) = \mathcal{O}(\sqrt{n \log \log n}),\; b_n = o(n), \textrm{ and } b_n \log \log n = o(n)$, we can finally we prove that $g_1(n), g_2(n), g_3(n) \to 0$ with probability 1, as $n \to \infty$. The proof is in Appendix subsection \ref{appendix:strong_consis}
\end{proof}

@@

\begin{proof}
\[
\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)
\]

Using theorem \ref{th:G-ACF_expec}, we can write the expectation of $\hat{\Gamma}_{G}$ as  a sum of equation \ref{eq:priestly} and some small order terms.
The proof is given in the Appendix subsection \ref{appendix:bias}.
\end{proof}

@@

\begin{proof}
Recall that $\tilde{\Sigma}$ is the averaged pseudo spectral variance estimator which uses the unobserved mean. Further, let $\tilde{\Sigma}^{ij}$ be the $(i,j)^{th}$ element of this matrix. We will prove that the variance of $\hat{\Sigma}_{G} \textrm{ and } \tilde{\Sigma}$ are equivalent for large sample sizes. The proof is in Appendix subsection \ref{appendix:variance}
\end{proof}

@@

\subsection{Bias of autocovariance} \label{appendix:bias}

@@

\begin{proof}[Proof of Theorem~\ref{th:G-_expec}]
\begin{align*}
    & \hat{\Gamma}_{G-,s}(k) \\
   & = \dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
    &= \left[\dfrac{1}{n} \sum_{t=1}^{n-|k|} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t=1}^{|k|} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right] \\ 
    & \quad +  \left[\dfrac{1}{n} \sum_{t=n-|k|+1}^{n}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right] + \left[\dfrac{n-|k|}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
    &= \hat{\Gamma}_s(k) - \dfrac{1}{n} \sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{n}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
\end{align*}
%
where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. We will study the expectations of the each of the above terms. Without loss of generality, consider $A_{11}$,
\begin{align*}
    &\E \left[A_{11} \right]\\
     &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
\end{align*}
%
Similarly,
%    
\begin{align}
\label{eq:acf_3}
    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k)^T - n\text{Var}\left[\bar{X}_1 \right] \right)\,.
    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
\end{align}

>>>>

\usepackage{amssymb,amsthm,amsmath}
\usepackage{commath,hyperref}
\usepackage{enumerate,xcolor}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{caption,setspace}
\usepackage{subcaption}
\DeclareMathOperator{\Tr}{Tr}
\newcommand{\dd}[1]{\mathrm{d}#1}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\text{Var}}
\newcommand{\Cov}{\text{Cov}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\B}{\mathcal{B}}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
% These three packages are from the American Mathematical Society and includes all of the important symbols and operations 
\usepackage{fullpage}
\usepackage{comment}
\usepackage[linesnumbered, ruled]{algorithm2e}
% By default, an article has some vary large margins to fit the smaller page format.  This allows us to use more standard margins.
\allowdisplaybreaks
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

@@

\begin{figure}[htbp]
\begin{subfigure}{\textwidth}
   \centering
   \includegraphics[width=.9\linewidth]{plots/gaussian-acf_n1e4.pdf}
   \caption{$n = 10^4$}
   \label{subfig:gauss-acf-1e4}
 \end{subfigure}\\
 \begin{subfigure}{\textwidth}
   \centering
   \includegraphics[width=.9\linewidth]{plots/gaussian-acf_n1e5.pdf} 
   \caption{$n = 10^5$}
   \label{subfig:gauss-acf-1e5}
 \end{subfigure}
 \caption{Autocorrelation plot for locally-centered ACF (left) and globally centered ACF (right) averaged over all chains. (a) $n = 10^4$, not converged yet; (b) $n =  10^5$, converged}
 \label{fig:gauss:acf}
\end{figure}
\end{example}

@@

 Suppose we have $m$ replications of Markov chains for same target distribution and $\{X_{st}; \; t \in \mathbb{Z}\}$ denote the $s^{th}$ Markov chain. Let the sample mean of $s^{th}$ Markov chain be denoted by $\bar{X}_s$ and the global mean by $\bar{\bar{X}} = \sum_{s = 1}^{m}\bar{X}_s/m$. The global mean provides a better estimate for the expectation value when the number of simulation per chain are not sufficient for the convergence to kick in. The globally-centered autocovariance function (G-ACF) for the $s^{th}$ Markov chain is given by:
%
\[
\hat{\Gamma}_{G,s}(k) = \dfrac{1}{n} \sum_{t=1}^{n-k}(X_{st}-\bar{\bar{X}})(X_{s(t+k)}-\bar{\bar{X}})^T
\]

@@

% \subsection{Theoretical results} % (fold)
% \label{sub:theoretical_results}

@@

The bias for G-ACF is similar to the bias of sample autocovariance estimator in case of single chain except for a few small order terms that shall be later addressed in theorem \ref{th:G-_expec}. Before getting to the bias results for $\hat{\Gamma}_{RAV}(k)$ for any lag $k$, we introduce an additional notation. For $q \geq 1$, we define
\[
\Phi^{(q)} = \sum\limits_{-\infty}^{\infty}\abs{k}^q \|\Gamma(k)\|
\]
We denote $\Phi^{(1)} \textrm{ by } \Phi$.

The proof of the following theorem is available in Appendix~\ref{appendix:bias}.
\begin{theorem} \label{th:G-_expec} Under stationarity,
\[
   \mathbb{E} \left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-2} \right)\,,
\]
and consequently,
\[
\mathbb{E} \left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}(k)_s \right] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,. 
\]
   % \[
   % \mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
   % \]
\end{theorem}

% \begin{proof}
%  The estimator for autocovariance with divisor $n$ is suggested by \cite{parzen1961approach} for its lesser mean square error despite having greater bias than the unbiased estimator with an $n - \abs{k}$ divisor. 
%  We know that $\hat{\Gamma}_s(k)$ is asymptotically unbiased with a $o(1)$ bias term that remains fixed for any $k$. The bias term is given by \cite{priestley1981spectral} as

%  \begin{equation} \label{eq:priestly}
%      \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
%  \right)
%  \end{equation}

% By proposition 1 in \cite{song1995optimal} 
% \begin{equation} \label{eq:song}
% \Var(\bar{X}) = \dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2} + o(n^{-2})
% \end{equation}

% As a consequence, if $\Var(\bar{X})$ is finite, then $\Var(\bar{X}) \to 0 \textrm{ as } n \to \infty$. We can break $\hat{\Gamma}_{G-}$ into four parts for all $k \geq 1$ as:
%  \[
%  \hat{\Gamma}_{G} =  \dfrac{1}{m}\sum_{s=1}^{m}\hat{\Gamma}_s(k) - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{mn}\sum_{s=1}^{m}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{mn}\sum_{s=1}^{m}(\bar{X}_s - \bar{\bar{X}})(\bar{X}_s - \bar{\bar{X}})^T\,,
%  \]
% %
% where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$\\
% The expectation value of the first term is given by equation \ref{eq:priestly} and \ref{eq:song} while the other three terms contribute $o(1)$ terms. The complete proof evaluating the expectation values of last three terms can be found in Appendix subsection \ref{appendix:bias}.
% \end{proof}

% \begin{remark} \label{rmrk:exp_G-f_minus_acf}
% Using theorem \ref{th:G_expec} and equation \ref{eq:priestly},
% \[
% \mathbb{E} \left[\hat{\Gamma}_{G}(k) - \hat{\Gamma}(k) \right] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
% \]
% We know that the sample autocovariance $\hat{\Gamma}(k)$ underestimates the truth due to a negative bias of $\abs{k}\Gamma(k)/n$ for finite $n$. However, in practice, it is preferred to overestimate the autocovariance for finite $n$ than to underestimate it in order to have a more realistic idea about the correlation in a Markov chain at a particular lag.  Note that the RHS in the above expression is positive. As a consequence, G-ACF will counter this negative bias and give more reliable estimates for ACF.

% \end{remark}

When $m = 1$, $\hat{\Gamma}_G(k)$ corresponds to $\hat{\Gamma}(k)$, the expectation of which can be found in \cite{priestley1981spectral}. Theorem~\ref{th:G-_expec} implies that the globally-centered autocovariances are asymptotically unbiased and exhibit reduced bias in finite samples compared to locally-centered autocovariances. The consequences of this are particularly pertinent for the diagonals of $\Gamma$. Special interest is also in the lag-0 autocovariance, that is, the variance of the target distribution.

\begin{corollary} \label{cor:lag0_expectation}
\[
\mathbb{E} \left[\hat{\Gamma}_{G}(0) \right] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
\]
\end{corollary}

\subsection{Autocorrelation} % (fold)
\label{sub:autocorrelation}

% subsection autocorrelation (end)
For any component $i$, the autocorrelation is
\[
\rho^{(i)}(k) = \dfrac{\Gamma^{(i)}(k)}{\Gamma^{(i)}(0)}\,,
\]
and is particularly useful for visualizing the serial correlation in components of the Markov chain. The typical estimate of the autocorrelation is constructed from  locally-centered autocovariance estimates which as was demonstrated in Section~\ref{sec:intro} can significantly underestimate the autocorrelation. 
\[
\hat{\rho}_{G,s}^{(i)}(k) = \dfrac{ \hat{\Gamma}^{(i)}_{G,s} (k)}{\hat{\Gamma}^{(i)}_{G,s} (0)}
\]
{\color{blue} Add more about autocorrelation}

% \begin{proof}
%  The proof is in Appendix subsection \ref{appendix:bias}.
% \end{proof}

@@

% \begin{proof}
% We complete the proof by showing that $\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij}$ converges to 0 almost surely for all $i,j \in \{1,...,p\}$ and $\tilde{\Sigma}^{ij} \to \Sigma^{ij}$ with probability 1 as $n \to \infty$. We will show that

% \[
% \hat{\Sigma}_{G-SVE}^{ij} - \tilde{\Sigma}^{ij} = g_1(n)D^2 + g_2(n)D + g_3(n)
% \]
% where $D$ is the finite random variable associated with SIP. We will show that
% \begin{align*}
%     g_1(n) &= (4+C_1)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2}\\
%     g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C_1)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
%     g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C_1)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right]
% \end{align*}

% Using $\psi(n) = \mathcal{O}(\sqrt{n \log \log n}),\; b_n = o(n), \textrm{ and } b_n \log \log n = o(n)$, we can finally we prove that $g_1(n), g_2(n), g_3(n) \to 0$ with probability 1, as $n \to \infty$. The proof is in Appendix subsection \ref{appendix:strong_consis}
% \end{proof}

@@

% \begin{proof}
% \[
% \mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = \sum_{k=-b_n+1}^{b_n-1} w\left(\dfrac{|k|}{b_n}\right)\mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] - \sum_{k=-\infty}^{\infty}\Gamma(k)
% \]

% Using theorem \ref{th:G-ACF_expec}, we can write the expectation of $\hat{\Gamma}_{G}$ as  a sum of equation \ref{eq:priestly} and some small order terms.
% The proof is given in the Appendix subsection \ref{appendix:bias}.
% \end{proof}

@@

% \begin{proof}
% Recall that $\tilde{\Sigma}$ is the averaged pseudo spectral variance estimator which uses the unobserved mean. Further, let $\tilde{\Sigma}^{ij}$ be the $(i,j)^{th}$ element of this matrix. We will prove that the variance of $\hat{\Sigma}_{G} \textrm{ and } \tilde{\Sigma}$ are equivalent for large sample sizes. The proof is in Appendix subsection \ref{appendix:variance}
% \end{proof}

@@

\subsection{Bias of Theorem~\ref{th:G-_expec}} 
\label{appendix:bias}

@@

\begin{proof}[Proof of Theorem~\ref{th:G-_expec}]
\begin{align*}
\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t=1}^{n-|k|} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
    &= \left[\dfrac{1}{n} \sum_{t=1}^{n-|k|} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t=1}^{|k|} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right] \\ 
    & \quad +  \left[\dfrac{1}{n} \sum_{t=n-|k|+1}^{n}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right] + \left[\dfrac{n-|k|}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
    &= \hat{\Gamma}_s(k) - \dfrac{1}{n} \sum_{t=1}^{|k|}A_{st}^T - \dfrac{1}{n}\sum_{t=n-|k|+1}^{n}A_{st} + \dfrac{n-|k|}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
\end{align*}
%
where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. We will study the expectations of the each of the above terms. Without loss of generality, consider $A_{11}$,
\begin{align*}
    &\E \left[A_{11} \right]\\
     &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
     % &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
    % &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
\end{align*}
%
Similarly,
%    
\begin{align}
\label{eq:acf_3}
    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k)^T - n\text{Var}\left[\bar{X}_1 \right] \right)\,.
    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
\end{align}
